Jager: Symbolic Specification-Based Program Adjustment

### 2013-05-01 paper/paper.tex
Removing the Evaluation and Related work sections for now because an evaluation is probably out of scope at this point and the related work gets enough coverage throughout the rest of the paper.
Removed the references section and replaced it with the bibliography tag which creates the references section automatically.
Adding a few paragraphs of future work.

\section{Evaluation}

\section{Related Work}

@@

@@

\section{References}

>>>>

%\section{Evaluation}

%\section{Related Work}

@@

There are a variety of ways in which Jager could be improved at this point.
These are all future work items which we will detail in this section. The
first of which would be to tie all the phases of Jager together so that they
can be performed automatically. Currently, each phase needs to be manually
invoked with the inputs relevant to that phase. We would like to add
connectors to all of the phases so that when one phase completes, its output
can be used to invoke the subsequent phase. This is mainly an engineering
task whereas the remaining future work items are related to the approach.

With respect to the trace generation phase, we are interested in exploring
ways in which less traces need to be generated. Our approach exhaustively
generates all traces for a program. While this may be feasible for the small
programs we have worked with, it could quickly becoming intractable for even
medium-sized programs. Existing program repair approaches do not suffer from
this kind of problem because they generate traces from test suites which
remain resonable in size even for large projects. It would be interesting to
see if there is some sweet spot sitting between the set of \emph{all} traces
through a program and the set of traces generated from a test suite.
Ideally, this sweet spot would be less computationally intensive than
generating all traces, but still provide better behavior coverage than a
traditional test suite.

During the trace differentiation phase and fault localization phase, we
identify \emph{good} and \emph{bad} traces and use them to localize faulty
program statements. In approaches that generate traces from test suites, we
can be reasonably sure that the traces represent interesting and relevant
paths through the program based on common use cases. However, with our
approach, we generate all traces, some of which may not be common or
interesting. Because of this, we believe it may be useful to consider ways
of weighting certain paths through the program

@@

\bibliographystyle{plain}
\bibliography{bib/paper}
